---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# prepair

<!-- badges: start -->
[![GitLab CI Build Status](https://gitlab.com/dickoa/prepair/badges/master/pipeline.svg)](https://gitlab.com/dickoa/prepair/pipelines)
[![Codecov Code Coverage](https://codecov.io/gl/dickoa/prepair/branch/master/graph/badge.svg)](https://codecov.io/gl/dickoa/prepair)
[![](http://www.r-pkg.org/badges/version/prepair)](http://www.r-pkg.org/pkg/prepair)
<!-- badges: end -->

An R package to repair broken GIS polygons using the [`prepair`](https://github.com/tudelft3d/prepair) Cpp library.

## Installation

You can install the development version of prepair from [Gitlab](https://gitlab.com/dickoa/prepair) using the `remotes` package with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_gitlab("dickoa/prepair")
```

## A quick Example

This is a basic example which shows you how to solve a common problem:

### A 'bowtie' polygon:

```{r p1}
library(prepair)
library(sf)

p1 <- st_as_sfc("POLYGON((0 0, 0 10, 10 0, 10 10, 0 0))")
st_is_valid(p1, reason = TRUE)
p11 <- st_prepair(p1)
st_is_valid(p11)

par(mfrow = c(1, 2))
plot(p1, main = "RAW")
plot(p11, main = "Repaired")
```

### Square with wrong orientation:

```{r p2}
p2 <- st_as_sfc("POLYGON((0 0, 0 10, 10 10, 10 0, 0 0))")
st_is_valid(p2, reason = TRUE)
```

### Inner ring with one edge sharing part of an edge of the outer ring:

```{r p3}
p3 <- st_as_sfc("POLYGON((0 0, 10 0, 10 10, 0 10, 0 0),(5 2, 5 7, 10 7, 10 2, 5 2))")
st_is_valid(p3, reason = TRUE)
p33 <- st_prepair(p3)
st_is_valid(p33)

par(mfrow = c(1, 2))
plot(p3, main = "RAW")
plot(p33, main = "Repaired")
```

### Dangling edge:

```{r p4}
p4 <- st_as_sfc("POLYGON((0 0, 10 0, 15 5, 10 0, 10 10, 0 10, 0 0))")
st_is_valid(p4, reason = TRUE)
p44 <- st_prepair(p4)
st_is_valid(p44)

par(mfrow = c(1, 2))
plot(p4, main = "RAW")
plot(p44, main = "Repaired")
```

### Two adjacent inner rings:

```{r p6}
p6 <- st_as_sfc("POLYGON((0 0, 10 0, 10 10, 0 10, 0 0), (1 1, 1 8, 3 8, 3 1, 1 1), (3 1, 3 8, 5 8, 5 1, 3 1))")
st_is_valid(p6, reason = TRUE)
p66 <- st_prepair(p6)
st_is_valid(p66)

par(mfrow = c(1, 2))
plot(p6, main = "RAW")
plot(p66, main = "Repaired")
```

### Polygon with an inner ring inside another inner ring:
```{r p7}
p7 <- st_as_sfc("POLYGON((0 0, 10 0, 10 10, 0 10, 0 0), (2 8, 5 8, 5 2, 2 2, 2 8), (3 3, 4 3, 3 4, 3 3))")
st_is_valid(p7, reason = TRUE)
p77 <- st_prepair(p7)
st_is_valid(p77)

par(mfrow = c(1, 2))
plot(p7, main = "RAW")
plot(p77, main = "Repaired")
```
