---
title: "1. Repair broken polygons with prepr"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{1. Repair broken polygons with prepr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%",
  dev = "svg")
```

## What is prepr ?

An R package to repair broken GIS polygons using the [`prepair`](https://github.com/tudelft3d/prepair) C++ library.

## prepr in action with simple polygons

This is a basic example which shows you how to solve a common problem:

### A 'bowtie' polygon:

```{r p1}
library(prepr)
library(sf)

p1 <- st_as_sfc("POLYGON((0 0, 0 10, 10 0, 10 10, 0 0))")
st_is_valid(p1, reason = TRUE)
p11 <- st_prepair(p1)
st_is_valid(p11)

st_as_text(p11)

par(mfrow = c(1, 2))
plot(p1, main = "RAW", col = "#D7722C")
plot(p11, main = "Repaired", col = "#D7722C")
```

### Square with wrong orientation:

```{r p2}
p2 <- st_as_sfc("POLYGON((0 0, 0 10, 10 10, 10 0, 0 0))")
st_is_valid(p2, reason = TRUE)
plot(p2, main = "RAW", col = "#D7722C")
```

### Inner ring with one edge sharing part of an edge of the outer ring:

```{r p3}
p3 <- st_as_sfc("POLYGON((0 0, 10 0, 10 10, 0 10, 0 0),(5 2, 5 7, 10 7, 10 2, 5 2))")
st_is_valid(p3, reason = TRUE)
p33 <- st_prepair(p3)
st_is_valid(p33)

st_as_text(p33)

par(mfrow = c(1, 2))
plot(p3, main = "RAW", col = "#D7722C")
plot(p33, main = "Repaired", col = "#D7722C")
```

### Dangling edge:

```{r p4}
p4 <- st_as_sfc("POLYGON((0 0, 10 0, 15 5, 10 0, 10 10, 0 10, 0 0))")
st_is_valid(p4, reason = TRUE)
p44 <- st_prepair(p4)
st_is_valid(p44)

st_as_text(p44)

par(mfrow = c(1, 2))
plot(p4, main = "RAW", col = "#D7722C")
plot(p44, main = "Repaired", col = "#D7722C")
```

### Two adjacent inner rings:

```{r p6}
p6 <- st_as_sfc("POLYGON((0 0, 10 0, 10 10, 0 10, 0 0), (1 1, 1 8, 3 8, 3 1, 1 1), (3 1, 3 8, 5 8, 5 1, 3 1))")
st_is_valid(p6, reason = TRUE)
p66 <- st_prepair(p6)
st_is_valid(p66)

st_as_text(p66)

par(mfrow = c(1, 2))
plot(p6, main = "RAW", col = "#D7722C")
plot(p66, main = "Repaired", col = "#D7722C")
```

### Polygon with an inner ring inside another inner ring:
```{r p7}
p7 <- st_as_sfc("POLYGON((0 0, 10 0, 10 10, 0 10, 0 0), (2 8, 5 8, 5 2, 2 2, 2 8), (3 3, 4 3, 3 4, 3 3))")
st_is_valid(p7, reason = TRUE)
p77 <- st_prepair(p7)
st_is_valid(p77)

st_as_text(p77)

par(mfrow = c(1, 2))
plot(p7, main = "RAW", col = "#D7722C")
plot(p77, main = "Repaired", col = "#D7722C")
```

## prepr in action with real datasets

### Reading the data

```{r read_data, cache = TRUE}
(clc1 <- read_sf("https://github.com/tudelft3d/prepair/raw/master/data/CLC2006_180927.geojson"))
(clc2 <- read_sf("https://github.com/tudelft3d/prepair/raw/master/data/CLC2006_2018418.geojson"))
par(mfrow = c(1, 2))
plot(st_geometry(clc1), main = "CLC2006_180927", col = 'lightblue', axes = TRUE, graticule = TRUE, lwd = 0.2, cex.axis = 0.5)
plot(st_geometry(clc2), main = "CLC2006_2018418", col = "lightblue", axes = TRUE, graticule = TRUE, lwd = 0.2, cex.axis = 0.5)
```

### Check if it's valid and repair it

```{r clean_it, cache = TRUE}
st_is_valid(clc1, reason = TRUE)
(clc1_rpr <- st_prepair(clc1))
st_is_valid(clc1_rpr)

st_is_valid(clc2, reason = TRUE)
(clc2_rpr <- st_prepair(clc2))
st_is_valid(clc2_rpr)
```

### How fast is `st_prepair` ?

`prepr::st_prepair` is fast and can be in some cases faster than `sf::st_make_valid`

```{r bench, cache = TRUE}
library(bench)
(bnch1 <- bench::mark(st_make_valid(clc1), st_prepair(clc1), check = FALSE))
summary(bnch1, relative = TRUE)

(bnch2 <- bench::mark(st_make_valid(clc2), st_prepair(clc2), check = FALSE))
summary(bnch2, relative = TRUE)
```

You also have cases where it's slower to `sf::st_make_valid`, let's use this data from a [closed issue](https://github.com/r-spatial/sf/issues/1280) in the `sf` R package.

```{r new_data, cache = TRUE}
## need vsicurl
(agb <- read_sf("/vsicurl/http://files.hawaii.gov/dbedt/op/gis/data/2015AgBaseline.shp.zip"))
all(st_is_valid(agb))
all(st_is_valid(st_make_valid(agb)))
all(st_is_valid(st_prepair(agb)))

plot(st_geometry(agb), main = "2015 Agriculture baseline", col = 'lightblue', axes = TRUE, graticule = TRUE, lwd = 0.2, cex.axis = 0.5)
```

`sf::st_make_valid` is faster with this data.


```{r bench2, cache = TRUE}
(bnch3 <- bench::mark(st_make_valid(agb), st_prepair(agb), check = FALSE))
summary(bnch3, relative = TRUE)
```

## Details and how to cite

Details of how we automatically repair broken polygons, and what results you can expect, are available in this scientific article by the original authors of `prepair`:

> Ledoux, H., Arroyo Ohori, K., and Meijers, M. (2014). A triangulation-based approach to automatically repair GIS polygons. *Computers & Geosciences* 66:121–131. [ [DOI] ](http://dx.doi.org/10.1016/j.cageo.2014.01.009) [ [PDF] ](http://3dgeoinfo.bk.tudelft.nl/hledoux/pdfs/14_cgeo_prepair.pdf)

If you use the R package `prepr` for a scientific project, please cite their original work.